\section{Summary}

\subsection{Review of Work Completed}
Throughout this Semester I set out to identify a problem within the \gls{Serverless} space. Upon identifying the problem a proposed solution was sought. This led to the identification of technologies which could solve the problem. A number of tools and methodologies were then chosen to help in the development of this solution. A number of design patterns were explored and looked at, resulting in the architecture seen in this report. Finally a benchmark prototype was built, with a second prototype being developed and improving on the benchmark set.
\subsection{Semester Two Work to Complete}
\label{sub:sem2}
With the prototype complete, and due to this project being Agile a backlog refinement meeting will be held with all stakeholders in this project to groom the backlog and make adjustments where needed that best suit the current state of the project. With the reduction of unknowns, work in Semester Two will be incremental releasable improvements on what is already complete.

There will be a local tech talk on Knative and building an optimal Function as a Container, held during Semester two. An Open Source Community release of the project will follow and will include a hackaton to gain valuable insights from the Kubernetes community on the product as a whole.

The intention is to complete the MVP stories and achieve all core functionality. Any stretch goals completed will be a bonus for this project and will serve as a launch point for community involvement.

