\section{Summary}
My main outcome to this assignment was to build confidence and refine my skill as an Android Developer. I feel I successfully achieved this and leave this semester confident in being able to take and complete any android task laid out in front of me.
\\There was multiple proud moments during the development of this application, one of which I mentioned already in incorporating both google sign in and firebase auth. Another was getting my head around the nav component and dealing with the challenges of AndroidX. All these moments added to building the confidence I strive for in my Android Development. 
\\The exposure to Kotlin was an enjoyable one, it is nice to sit back and compare and contrast differences between paradigms. Seeing how Kotlin leverages Java, abstracting away the boring boilerplate required by Java and allowing my to focus on the task at hand.
\\Mentioned a few times in this document is the complexity that is abstracted under the hood in Android away from the developer. While giving us the freedom to plug into the powerful underlying architecture and features Android has to offer. I was often left asking myself, how did Android become so popular? Before we had these support libraries, how did developers go about building apps. The complexity of leveraging core components within Android must have been massive. So for the work on the support libraries, and AndroidX, I definitely am grateful as they make developing on Android an enjoyable experience. 