\section{Introduction}
Modern cloud centric computing has seen a number of technologies and approaches emerge as candidates for auto inclusion in development stacks. In particular,  Kubernetes and developing for a serverless world are fast becoming the de facto way of working as their benefits are clear. Simple, yet clever configurations can bring unrivalled scalability, coupled with huge cost saving over the lifecycle of a service. These are among the primary drivers for attracting developers towards this paradigm.
\\Through this trend a number of Frameworks and Models have emerged, which allow developers build modern applications. In paticular and the focus of this report is Knative.
\\Knative is comprised of middleware components which are essential to build modern, source-centric, and container-based applications. By abstracting away the "boring" bits Knative frees developers to focus on writing interesting code.
\subsection{Outline}
This paper will be broken into two sections, Theory and Practical. Throughout the Theory section we will answer numerous common questions around Knative, gaining an understanding of the framework. Finally in the Practical section we will get our hands dirty with Knative, by exploring their documentation, installing and deploying example applications and digging deeper into what Knative have to offer. We will finish with taking the Knative approach to building a modern serverless web application. The paper will be wrapped up with a Summary and my thoughts on Knative as a solution to serverless deployments within Kubernetes.